---
title: "Developing Data Product Course Project"
author: "Marsela Yulita"
date: "October 4, 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

This presentation is part of peer-graded assignment of the Developing Data Product Course, held by Johns Hopkins University and Coursera. This peer assessed assignment has two parts. 

- Create a Shiny application and deploy it on Rstudio's servers. 
- Use Slidify or Rstudio Presenter to prepare a reproducible pitch presentation about the application.

## The Mtcars Application

This application based on dataset mtcars from R. The application can be access in [shinyapps](https://myulita.shinyapps.io/mtcarsapp/).

This application allows users to input several car specification, to get a list of car model with gas cost calculation for daily distance traveled. This apps show the plots for a variation values of Horsepower and Weight compared with Gas Cost. with assumption gass price per gallon is US$ 2.55.

The reason i chose mtcars dataset, just because mtcars dataset available and ready to use on R without any prior packages installation. So it will easy for everyone to reproduce this application.

## Input - Output

Users allows to update these variables:

- Number of Cylinder
- Transmission type
- Daily Distance
- Gross Horsepower
- Weight

The application outputs:

- Data
- Plot

The source code for ui.R and sever.R files are available on the [Git Hub](https://github.com/coursera-my/developing-data-product).

## The Data

The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973-74 models).

```{r cars, echo = TRUE}
head(mtcars)
```


